### 2019-06-25 TFM.tex
Adiós

\documentclass[11pt,notitlepage]{report}

\usepackage[left=4cm,right=4cm,top=3cm,bottom=3cm]{geometry}
\usepackage{graphicx}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
%\usepackage{color}
\usepackage{float}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{chngcntr}

\counterwithout{equation}{section}
\counterwithout{equation}{chapter}

@@

\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{fact}{Fact}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{propdef}{Proposition / Definition}[chapter]
\newtheorem{remark}{Remark}[chapter]

@@

\begin{document}
\begin{abstract}
	The goal is to generalize the results from Lynch (1992) on the convergence law for sparse random graphs to sparse random hypergraphs. This requires in particular an understanding of Lynch's techniques, based on Ehrenfeucht-Fraïssé games, an analysis of the structure of sparse random hypergraphs.
\end{abstract}
\tableofcontents

\chapter*{Introduction}

\chapter{Preliminaries}

\section{Models of Random Graphs}

\section{First Order Logic}

\section{Ehrenfeucht Fraisse Games and the Logic of Random Graphs}

\chapter{Probabilities of Sentences about Very Sparse Random Graphs}

In this chapter we will review the results obtained
 in the paper with the same name by James F. Lynch \cite{lynch1992probabilities}.
In there, limit probabilities of sentences in the first order language of graphs $\mathcal{L}$
are discussed for the binomial model $G(n,p)$ in the cases $p=\beta/n$ and
$p=\beta n^{-\alpha}$ with $\alpha=(l+1)/l$ . \par

More precisely, it is proven that in those cases the 
probability of every sentence converges and it is shown
that for any of those sentences, its limit probability 
is among the values taken by some analytic formulas
with parameter $\beta$. \par

We are interested in the case $p=\frac{\beta}{n}$, which is 
the one discussed more extensively in \cite{lynch1992probabilities}. 
According to the author, the relevant theorems for 
the other case can be proven analogously. From now on we
will only refer as random graphs to the ones in $G(n,\beta/n)$\par

From now on we will denote by $Poi_\lambda$ the probability
function of the Poisson distribution with mean $\lambda$.
That is, the one given by $Poi_\lambda(n)=e^{-\lambda}\lambda^n/n!$ 
for any $n\in \N$.
Also, we define $Poi_\lambda(\leq n)$ and $Poi_\lambda(>n)$ as 
$\sum_{i=0}^n Poi_\lambda(n)$ and $1-Poi_\lambda(\leq n)$
respectively. Notice that for a fixed $n$, both $Poi_\lambda(\leq n)$ 
and $Poi_\lambda(>n)$ can be considered real functions of parameter $\lambda$. \par

We define the following sets of functions. Let $\Lambda$ be the smallest 
set of expressions with parameter $\beta$ such that:

\begin{itemize}[noitemsep, topsep=0pt]
	\item $1\in \Lambda$,
	\item For any $\lambda \in \Lambda$ and $i\in \N$, 
	both $Poi_{\beta\lambda}(n)$ and $Poi_{\beta\lambda}(> n)$ are in
	$\Lambda$.
	\item For any $\lambda_1,\lambda_2 \in \Lambda$,
	$\lambda_1 \lambda_2$ belongs to $\Lambda$ as well.
\end{itemize}

And let $\Theta$ be the smallest set of functions with parameter $\beta$
such that:
\begin{itemize}[noitemsep, topsep=0pt]
	\item For any $\lambda \in \Lambda$ 
	and $n,a,i\in \N$, with $i\geq 3$, 
	both $Poi_{\beta^i\lambda/a}(\leq n)$ and $Poi_{\beta^i\lambda/a}(> n)$
	are in $\Theta$.
\end{itemize}

The main result is the following:

\begin{theorem}[Lynch, 1992] \label{thrm:main}
	Let $\phi$ be a sentence in the first order theory of graphs. Then the limit
	$\lim\limits_{n\to \infty} P(G(n,\beta/n) \models \phi )$ exists for all positive real numbers
	$\beta$, and it is a finite sum of expressions in $\Theta$.
\end{theorem}

We show now an outline of the proof. \par 
We show that for any quantifier rank $k$ there are some classes of graphs 
$C^k_1,\dots, C^k_{n_k}$ such that
\begin{itemize}[noitemsep, topsep=0pt]
	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
	\item[(2)] a.a.s. any random graph belongs to some of them, and
	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
\end{itemize}

After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
$G$ a random graph in $G(n,\beta/n)$. \par

The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
allow ourselves to just sketch some of the proofs during this chapter.

\section{Agreeability Classes}

It is known that $n^{-v/e}$ is the t
hreshold probability for the appearance 
of a balanced graph of density $v/e$. 
In our case $v/e=1$, so in consequence any connected graph $H$
with $e(H)< v(H)$ a.a.s will not appear 
as a subgraphs of $G(n,\beta/n)$. It can be easily 
shown that such graphs $H$ are exactly 
the ones containing more than one cycle. \par

If $H$ is a connected graph with $v=e$, then $H$ is an uni-cyclic graph.
In this case, the number $X_H$ of copies of $H$ 
in $G(n,\beta/n)$ will asymptotically have non-zero bounded expectancy $m$. 
It does not take much work to prove, using Brun's sieve, 
that $X_H$ converges in distribution to a Poisson 
random variable with mean $m$ as $n$ goes to infinity.  \par

Finally, if $H$ is a connected graph 
with $v>e$ then it must be a tree. Here 
the expected number of copies of $H$ 
in $G(n,\beta/n)$ diverges asymptotically. 
Informally, trees of any kind will occur arbitrarily often. \par

This all means, in a sense, that a.a.s the only 
difference between large graphs in $G(n,\beta/n)$
lies in their uni-cyclic subgraphs. More precisely,
because of the ``locality" of first order logic of quantifier 
rank $k$ we will only be interested in the 
``small`` neighborhoods of the ``short" cycles.  
Thus, our goal will be to classify uni-cyclic graphs
in a way that respects equivalence under first 
order logic of quantifier rank $k$. \par
~\par
To make our classification suitable for proofs 
involving E.F. games we need to work graphs to which we ``attach" labels. 
We define the set of symbols $Const=\{c_i\}_{i\in \N}$ 
as the set of constants. Also, we will denote by
$Const_n$ the set $\{c_1,\dots, c_n\}$.

\begin{definition} 
	A \textbf{co-labeling} of a graph $G=(V,E)$ is a map 
	$\sigma: D\rightarrow V$, where $D\subset C$ is a 
	finite set of constant symbols. Given $c_i\in D$, 
	we will say that the vertex $\sigma(c_i)$ is labeled $c_i$.
	Equivalently, we can denote a labeling $\sigma$ as a tuple
	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ where each $c_{i_j}$
	 is a constant symbol, and $x_j$ is the vertex
	in $V$ labeled $c_{i_j}$.
\end{definition}

\begin{definition} 
	A \textbf{graph with constants}\footnote{
		Compare with \cite{lynch1992probabilities}, where they are called ``rooted graphs". 
		}
	$G(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ 
	is a graph $G$ together with a co-labeling 
	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$. 
\end{definition}

To keep our notation compact we will often drop 
he $x_i$'s and say $G(c_{i_1},\dots, c_{i_m})$. \par

\begin{definition}
Let $G$ be a graph with constants. A subgraph $H$ of $G$ is
a graph with constants such that $V(H)\subseteq V(G)$, $E(H)\subseteq E(G)$ and 
all vertices in $V(H)$ have the same labels in $H$ and $G$. 
\end{definition}

An important abuse of notation we are going to make
will be to identify the constants $c_i$ with their labeled
vertices $\sigma(c_i)$. This way things like $c_i\sim c_j$ 
will make sense. In this context, notice that the expression
$c_i=c_j$ is ambiguous because the vertices labeled $c_i$ and $c_j$ 
may be the same for some $i\neq j$, but 
the constant symbols $c_i$ and $c_j$ will be equal only if $i=j$. 
We will make sure to leave no room for ambiguity in this situations. \par

\begin{propdef}
	Let $G=(V,E,\clist)$ be a connected graph with constants. Then it has a unique minimal
	connected subgraph $H$ containing all its constants and cycles.
	We will call the \textbf{center} of $G$ to such subgraph and denote it by $Center(G)$.
	If $\bar{G}$ is an arbitrary graph with constants, then its center $Center{\bar{G}}$ will
	be the union of the centers of its connected components. 
\end{propdef}
\begin{proof}
	TO DO
\end{proof}

For an arbitrary graph with constants we define the metric $d(\cdot,\cdot)$ on $V(G)$ 
as the one such that $d(x,y)$ is the minimum length of a path connecting
$x$ and $y$ in $G$ or $\infty$ if such path does not exist. 
For any vertex $x\in V(G)$ and $r\in \N$ we define the co-labeled
subgraph $N(x;r)$ as the ball of radius $r$ centered at $v$. 
That is, the induced subgraph with vertex set
\[ V(N(x;r))= \{\, y\in V \, | \, d(x,y)\leq  r \,	\}.\] 
In a similar vein, given $X\subseteq V(G)$ we define its neighborhood of radius $r$ as
the induced co-labeled subgraph $N(X;r)$ whose vertex set is
\[ V(N(X;r))= \{\, y\in V \, | \, \forall x\in X: \, \,  d(x,y)\leq  r \,	\}.\]  
\par

Let $G=(V,E)$, and $V^\prime\subseteq V$. Another important abuse 
of notation we will make is writing $H=(V^\prime, E)$ 
for a subgraph $H$ to mean that the edge set of $E(H)$ is the one
induced by $E(G)$ on $V^\prime$.

\begin{definition} 
	A \textbf{rooted tree} $T=(V,E,x)$ is a tree 
	$(V,E)$ with distinguished vertex $x\in V$ with we will call 
	\textbf{root} of the tree.
\end{definition}

\begin{propdef}
	Let $G=(V,E,\clist)$ be a connected graph and $x\in V$. 
	Then define $Tree(x,G)$	as the rooted tree
	\[Tree(x,G) = (V_x,E,x),\] where
	\[V_x= \{\, y\in V \, | \,\,d(Center(G),y) = d(Center(G),x) + d(x,y) \}.\]

\end{propdef}
\begin{proof}
	TO DO
\end{proof}

The radius $r(T)$ of a rooted tree $T=(V,E,x)$
is the maximum distance between its root $x$ and any other of
its vertices. The branches of $T$ are the rooted trees of the form
$Tree(y,T)$, where $y\sim x$. We will denote by $Br(T)$ the set of
branches of $T$. \par

We begin by defining an equivalence relation between rooted 
trees for each quantifier rank $k$.

\begin{definition} 
	Let $k\in \N$ with $k\geq 1$. The \textbf{k-morphism} equivalence relation
	$\morph{k}$ between
	graph with constantss is the one inductively defined as follows:
	\begin{itemize}
		\item If $T_1, T_2$ are rooted trees of radius $0$ -i.e., they
		consist only of their roots- they are $k$-morphic. 
		\item Let $T_1, T_2$ be rooted trees of radius $r$ whose 
		rots have the same label. Then $T_1 \morph{k} T_2$ if 
		for any $k$-morphism class $C$ of trees with
		radius less than $r$ and root either
		\begin{center}
			\vspace{-0.2cm}
			``$T_1$ and $T_2$ have the same number of branches of type $C$"
		\end{center}
		\vspace{-0.3cm}
		\[ |Br(T_1)\cap C| = |Br(T_2)\cap C|,\]
		or 
		\begin{center}
			\vspace{-0.2cm}
			``$T_1$ and $T_2$ have both more than $k$ branches of type $C$"
		\end{center}
	\vspace{-0.3cm}
		\[ |Br(T_i)\cap C| \geq k+1 \text{ for } i=1,2. \]
	\end{itemize} 
\end{definition}

It follows from the definition that $k$-morphic trees have the same radius. 
It is also easy to check that the $k$-morphism relation is indeed an equivalence one.

\begin{proposition}
	For all $k,r\in N$ and with $k\geq 1$, the set of classes of $k$-morphic trees
	with radius lesser or equal than $r$ is finite.
\end{proposition}
\begin{proof}
TO DO
\end{proof}

We define now the $k$-morphism relation for arbitrary graph with constantss. 
%If $G^1=(V^1,E^1,\clist)$ and $G^2=(V^2,E^2,\clist)$ are graph with constantss with
%the same constants, to avoid confusion we will denote by $c_{i_j}^1$ and $c_{i_j}^2$
%the vertices labeled $c_{i_j}$ in $G^1$ and $G^2$ respectively.

\begin{definition}
	Let $G^1=(V^1,E^1,c_{i_1}[x^1_1],\dots, c_{i_m}[x_m^1])$ and  $G^2=(V^2,E^2,c_{i_1}[x^1_2],$ 
	$\dots, c_{i_m}[x_m^2])$ be graph with constantss with the same constant symbols. 
	We will say that they are $k$-morphic (denoted by $G^1 \morph{k}G^2$) if there is
	a bijection $f: V(Center(G^1))\rightarrow V(Center(G^2))$ such that
	\begin{itemize}
		\item ``$f$ preserves edges"
		\[\forall x,y\in V(Center(G^1)): \quad  x\sim y \iff f(x)\sim f(y). \]
		\item ``$f$ preserves labels"
		\[\forall j\in \{1,\dots,m\}: \quad f(x^1_j) = x^2_j.\]
		\item ``$f$ preserves $k$-morphism classes of trees"
		\[\forall x\in V(Center(G^1)): \quad  Tree(x,G^1)\morph{k} Tree(f(x),G^2).\]
	\end{itemize}
	In this case we will say that $G^1 \morph{k} G^2$ via $f$. 	
\end{definition}

We are going to show that the rank $k$ type of a random graph a.a.s only 
depends on the neighborhoods of its small cycles. In consequence the following definition
is motivated:

\begin{definition} 
	Let $G=(V,E,\clist)$ be a graph with constants. Then its core of radius $r$, $Core(G,r)$
	is the co-labeled subgraph $N(X;r)$, where $X$ is the union of the (vertex sets of the)
	cycles in $G$ with size at most $2r+1$ and all of the labeled vertices in $G$. 
\end{definition}

\chapter{First Order Logic of Sparse Random Hypergraphs}

@@

\begin{definition} 
	Let $p=(p_1,\dots, p_c)$, where all $p_i$'s are real numbers
	between $0$ and $1$. 
	The random model $HG(n,p)$ with edge colors $1,\dots,c$,
	sizes $a_1,\dots,a_c$, 
	symmetry groups $\Phi_1,dots,\Phi_c$ 
	and restrictions $A_1,\dots,A_c$, is the one that
	assigns to each graph $G=([n], H_1,\dots, H_c)$
	probability
	\[ Pr(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
	\]
	Equivalently, this is the probability space obtained by 
	assigning to each colored edge 
	$e\in \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ probability $p_i$ independently. 
\end{definition}

@@

\section{The Theorem.}

>>>>

\documentclass[11pt,notitlepage,a4paper]{article}

\usepackage[left=3.7cm,right=3.7cm,top=3cm,bottom=3cm]{geometry}
\usepackage{graphicx}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
%\usepackage{color}
\usepackage{float}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{chngcntr}
\usepackage{cleveref}
\usepackage{pdfpages}

\counterwithout{equation}{section}

@@

\newtheorem{proposition}{Proposition}[section]
\newtheorem{fact}{Fact}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{propdef}{Proposition / Definition}[section]
\newtheorem{remark}{Remark}[section]

@@

\begin{document}

	\includepdf{Portada.pdf}

\begin{abstract}
	We give a generalization the results from Lynch in \cite{lynch1992probabilities}
	on the convergence law for sparse random graphs to sparse random hypergraphs.
\end{abstract}
\clearpage
\tableofcontents
\clearpage

\section*{Introduction}

This work is the thesis presented for the Master in Applied Mathematics and 
Mathematical Engineering of the Universitat Politècnica de Catalunya in 
June 2019. \par

This text belongs to the study of the asymptotic properties of random structures.
This is an active area of mathematics that has gained recent popularity due to 
the increasing need for methods that allow for analysis of large random
structures. These structures appear in a wide array of 
``real-life" problems, ranging
from the study of social networks to biology, and they are
arguably interesting in their own right.\par

The objective of this work, proposed by Marc Noy and Albert Atserias, was 
to generalize the results obtained in \cite{lynch1992probabilities} to more
general random structures. This was motivated by applications to the study
of the satisfability of random CNF formulas, but those are out of the scope of 
this work. \par

Going into further detail, in \cite{lynch1992probabilities} the asymptotic 
behavior under first order logic of the Erdös-Rényi binomial model $\mathcal{G}(n,p)$, where
$p$ is taken as a decreasing function on $n$ of the form $\beta\cdot n^{-1}$,
is studied. The first order properties of graphs are the ones expressible in 
terms of quantification over vertices and Boolean combinations of statements 
of the form ``$x$ adjacent to $y$'' and  ``$x$ equal to $y$''. The main theorem
in \cite{lynch1992probabilities} states that the limit probability that a graph
in $\mathcal{G}(n,\beta/n)$ satisfies any given first-order property exists
and has good properties with respect to $\beta$. \par

The original goal was to give generalizations for the case of uniform hypergraphs
but the techniques used for that case also allowed for generalizations to 
hypergraphs with multiple edge sets of different sizes.

\clearpage

\section{Logic of Sparse Random Graphs}

We give a brief overview of \cite{lynch1992probabilities}.
The asymptotic behavior of graphs in $G(n,\beta/n)$ is as follows
	\begin{itemize}
	\item The number of cycles of 
	length $3,4\dots, r$
	are asymptotically distributed like independent Poisson 
	variables.
	\item Small cycles are a.a.s (asymptotically almost surely) far away.
	\item Fixed vertices are a.a.s far away.
	\item The ball of a given radius centered in fixed
	vertex is a.a.s a tree. Any tree occurs with a positive 
	probability.
\end{itemize}

This way, asymptotically, trees of any kind occur arbitrarily often in a typical
random graph. Given the locality of first order logic up to a fixed 
quantifier rank this is tells us that the only thing that the only way 
to distinguish large random graphs in $G(n,\beta/n)$ 
(up to a fixed quantifier rank) 
is by looking at the neighborhoods of their small cycles. \par

It is given a finite and exhaustive classification of the uni-cyclic
graphs with less than a given radius. After that it is shown that
if two graphs $G_1$ and $G_2$ contain the same number 
of uni-cycles of each type or they
contain a large enough number of those then they are a.a.s equivalent
under first order logic up to some quantifier rank $k$. This is done by giving
a winning strategy for duplicator in the E.F. game of $k$ round played on 
$G_1$ and $G_2$.\par

Finally it is shown that the numbers of uni-cycles of each type contained in
a random graph are asymptotically distributed like independent Poisson variables 
whose means are given by some other nested ``Poisson expressions" that correspond 
to the trees hanging from each uni-cycle.

%In this chapter we will review the results obtained
% in the paper with the same name by James F. Lynch \cite{lynch1992probabilities}.
%In there, limit probabilities of sentences in the first order language of graphs $\mathcal{L}$
%are discussed for the binomial model $G(n,p)$ in the cases $p=\beta/n$ and
%$p=\beta n^{-\alpha}$ with $\alpha=(l+1)/l$ . \par
%
%More precisely, it is proven that in those cases the 
%probability of every sentence converges and it is shown
%that for any of those sentences, its limit probability 
%is among the values taken by some analytic formulas
%with parameter $\beta$. \par
%
%We are interested in the case $p=\frac{\beta}{n}$, which is 
%the one discussed more extensively in \cite{lynch1992probabilities}. 
%According to the author, the relevant theorems for 
%the other case can be proven analogously. From now on we
%will only refer as random graphs to the ones in $G(n,\beta/n)$\par
%
%From now on we will denote by $\mathrm{Poiss}_\lambda$ the probability
%function of the Poisson distribution with mean $\lambda$.
%That is, the one given by $\mathrm{Poiss}_\lambda(n)=e^{-\lambda}\lambda^n/n!$ 
%for any $n\in \N$.
%Also, we define $\mathrm{Poiss}_\lambda(\leq n)$ and $\mathrm{Poiss}_\lambda(>n)$ as 
%$\sum_{i=0}^n \mathrm{Poiss}_\lambda(n)$ and $1-\mathrm{Poiss}_\lambda(\leq n)$
%respectively. Notice that for a fixed $n$, both $\mathrm{Poiss}_\lambda(\leq n)$ 
%and $\mathrm{Poiss}_\lambda(>n)$ can be considered real functions of parameter $\lambda$. \par
%
%We define the following sets of functions. Let $\Lambda$ be the smallest 
%set of expressions with parameter $\beta$ such that:
%
%\begin{itemize}[noitemsep, topsep=0pt]
%	\item $1\in \Lambda$,
%	\item For any $\lambda \in \Lambda$ and $i\in \N$, 
%	both $\mathrm{Poiss}_{\beta\lambda}(n)$ and $\mathrm{Poiss}_{\beta\lambda}(> n)$ are in
%	$\Lambda$.
%	\item For any $\lambda_1,\lambda_2 \in \Lambda$,
%	$\lambda_1 \lambda_2$ belongs to $\Lambda$ as well.
%\end{itemize}
%
%And let $\Theta$ be the smallest set of functions with parameter $\beta$
%such that:
%\begin{itemize}[noitemsep, topsep=0pt]
%	\item For any $\lambda \in \Lambda$ 
%	and $n,a,i\in \N$, with $i\geq 3$, 
%	both $\mathrm{Poiss}_{\beta^i\lambda/a}(\leq n)$ and $\mathrm{Poiss}_{\beta^i\lambda/a}(> n)$
%	are in $\Theta$.
%\end{itemize} 
%
%The main result is the following:
%
%\begin{theorem}[Lynch, 1992] \label{thrm:main}
%	Let $\phi$ be a sentence in the first order theory of graphs. Then the limit
%	$\lim\limits_{n\to \infty} P(G(n,\beta/n) \models \phi )$ exists for all positive real numbers
%	$\beta$, and it is a finite sum of expressions in $\Theta$.
%\end{theorem}
%
%We show now an outline of the proof. \par 
%We show that for any quantifier rank $k$ there are some classes of graphs 
%$C^k_1,\dots, C^k_{n_k}$ such that
%\begin{itemize}[noitemsep, topsep=0pt]
%	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
%	\item[(2)] a.a.s. any random graph belongs to some of them, and
%	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
%\end{itemize}
%
%After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
%in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
%$G$ a random graph in $G(n,\beta/n)$. \par
%
%The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
%that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
%allow ourselves to just sketch some of the proofs during this chapter. 
%
%\section{Agreeability Classes}
%
%
%It is known that $n^{-v/e}$ is the t
%hreshold probability for the appearance 
%of a balanced graph of density $v/e$. 
%In our case $v/e=1$, so in consequence any connected graph $H$
%with $e(H)< v(H)$ a.a.s will not appear 
%as a subgraphs of $G(n,\beta/n)$. It can be easily 
%shown that such graphs $H$ are exactly 
%the ones containing more than one cycle. \par
%
%If $H$ is a connected graph with $v=e$, then $H$ is an uni-cyclic graph.
%In this case, the number $X_H$ of copies of $H$ 
%in $G(n,\beta/n)$ will asymptotically have non-zero bounded expectancy $m$. 
%It does not take much work to prove, using Brun's sieve, 
%that $X_H$ converges in distribution to a Poisson 
%random variable with mean $m$ as $n$ goes to infinity.  \par
%
%Finally, if $H$ is a connected graph 
%with $v>e$ then it must be a tree. Here 
%the expected number of copies of $H$ 
%in $G(n,\beta/n)$ diverges asymptotically. 
%Informally, trees of any kind will occur arbitrarily often. \par
%
%This all means, in a sense, that a.a.s the only 
%difference between large graphs in $G(n,\beta/n)$
%lies in their uni-cyclic subgraphs. More precisely,
%because of the ``locality" of first order logic of quantifier 
%rank $k$ we will only be interested in the 
%``small`` neighborhoods of the ``short" cycles.  
%Thus, our goal will be to classify uni-cyclic graphs
%in a way that respects equivalence under first 
%order logic of quantifier rank $k$. \par
%~\par
%To make our classification suitable for proofs 
%involving E.F. games we need to work graphs to which we ``attach" labels. 
%We define the set of symbols $Const=\{c_i\}_{i\in \N}$ 
%as the set of constants. Also, we will denote by
%$Const_n$ the set $\{c_1,\dots, c_n\}$.
% 
%\begin{definition} 
%	A \textbf{co-labeling} of a graph $G=(V,E)$ is a map 
%	$\sigma: D\rightarrow V$, where $D\subset C$ is a 
%	finite set of constant symbols. Given $c_i\in D$, 
%	we will say that the vertex $\sigma(c_i)$ is labeled $c_i$.
%	Equivalently, we can denote a labeling $\sigma$ as a tuple
%	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ where each $c_{i_j}$
%	 is a constant symbol, and $x_j$ is the vertex
%	in $V$ labeled $c_{i_j}$.
%\end{definition}
%
%\begin{definition} 
%	A \textbf{graph with constants}\footnote{
%		Compare with \cite{lynch1992probabilities}, where they are called ``rooted graphs". 
%		}
%	$G(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ 
%	is a graph $G$ together with a co-labeling 
%	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$. 
%\end{definition}
%
%To keep our notation compact we will often drop 
%he $x_i$'s and say $G(c_{i_1},\dots, c_{i_m})$. \par
%
%\begin{definition}
%Let $G$ be a graph with constants. A subgraph $H$ of $G$ is
%a graph with constants such that $V(H)\subseteq V(G)$, $E(H)\subseteq E(G)$ and 
%all vertices in $V(H)$ have the same labels in $H$ and $G$. 
%\end{definition}
%
%
%An important abuse of notation we are going to make
%will be to identify the constants $c_i$ with their labeled
%vertices $\sigma(c_i)$. This way things like $c_i\sim c_j$ 
%will make sense. In this context, notice that the expression
%$c_i=c_j$ is ambiguous because the vertices labeled $c_i$ and $c_j$ 
%may be the same for some $i\neq j$, but 
%the constant symbols $c_i$ and $c_j$ will be equal only if $i=j$. 
%We will make sure to leave no room for ambiguity in this situations. \par
%
%
%\begin{propdef}
%	Let $G=(V,E,\clist)$ be a connected graph with constants. Then it has a unique minimal
%	connected subgraph $H$ containing all its constants and cycles.
%	We will call the \textbf{center} of $G$ to such subgraph and denote it by $Center(G)$.
%	If $\bar{G}$ is an arbitrary graph with constants, then its center $Center{\bar{G}}$ will
%	be the union of the centers of its connected components. 
%\end{propdef}
%\begin{proof}
%	TO DO
%\end{proof}
%
%For an arbitrary graph with constants we define the metric $d(\cdot,\cdot)$ on $V(G)$ 
%as the one such that $d(x,y)$ is the minimum length of a path connecting
%$x$ and $y$ in $G$ or $\infty$ if such path does not exist. 
%For any vertex $x\in V(G)$ and $r\in \N$ we define the co-labeled
%subgraph $N(x;r)$ as the ball of radius $r$ centered at $v$. 
%That is, the induced subgraph with vertex set
%\[ V(N(x;r))= \{\, y\in V \, | \, d(x,y)\leq  r \,	\}.\] 
%In a similar vein, given $X\subseteq V(G)$ we define its neighborhood of radius $r$ as
%the induced co-labeled subgraph $N(X;r)$ whose vertex set is
%\[ V(N(X;r))= \{\, y\in V \, | \, \forall x\in X: \, \,  d(x,y)\leq  r \,	\}.\]  
%\par
%
%Let $G=(V,E)$, and $V^\prime\subseteq V$. Another important abuse 
%of notation we will make is writing $H=(V^\prime, E)$ 
%for a subgraph $H$ to mean that the edge set of $E(H)$ is the one
%induced by $E(G)$ on $V^\prime$.
%
%\begin{definition} 
%	A \textbf{rooted tree} $T=(V,E,x)$ is a tree 
%	$(V,E)$ with distinguished vertex $x\in V$ with we will call 
%	\textbf{root} of the tree.
%\end{definition}
%
%\begin{propdef}
%	Let $G=(V,E,\clist)$ be a connected graph and $x\in V$. 
%	Then define $Tree(x,G)$	as the rooted tree
%	\[Tree(x,G) = (V_x,E,x),\] where
%	\[V_x= \{\, y\in V \, | \,\,d(Center(G),y) = d(Center(G),x) + d(x,y) \}.\]
%
%\end{propdef}
%\begin{proof}
%	TO DO
%\end{proof}
%
%
%
%The radius $r(T)$ of a rooted tree $T=(V,E,x)$
%is the maximum distance between its root $x$ and any other of
%its vertices. The branches of $T$ are the rooted trees of the form
%$Tree(y,T)$, where $y\sim x$. We will denote by $Br(T)$ the set of
%branches of $T$. \par
%
%We begin by defining an equivalence relation between rooted 
%trees for each quantifier rank $k$.
%
%\begin{definition} 
%	Let $k\in \N$ with $k\geq 1$. The \textbf{k-morphism} equivalence relation
%	$\morph{k}$ between
%	graph with constantss is the one inductively defined as follows:
%	\begin{itemize}
%		\item If $T_1, T_2$ are rooted trees of radius $0$ -i.e., they
%		consist only of their roots- they are $k$-morphic. 
%		\item Let $T_1, T_2$ be rooted trees of radius $r$ whose 
%		rots have the same label. Then $T_1 \morph{k} T_2$ if 
%		for any $k$-morphism class $C$ of trees with
%		radius less than $r$ and root either
%		\begin{center}
%			\vspace{-0.2cm}
%			``$T_1$ and $T_2$ have the same number of branches of type $C$"
%		\end{center}
%		\vspace{-0.3cm}
%		\[ |Br(T_1)\cap C| = |Br(T_2)\cap C|,\]
%		or 
%		\begin{center}
%			\vspace{-0.2cm}
%			``$T_1$ and $T_2$ have both more than $k$ branches of type $C$"
%		\end{center}
%	\vspace{-0.3cm}
%		\[ |Br(T_i)\cap C| \geq k+1 \text{ for } i=1,2. \]
%	\end{itemize} 
%\end{definition}
%
%It follows from the definition that $k$-morphic trees have the same radius. 
%It is also easy to check that the $k$-morphism relation is indeed an equivalence one. 
%
%\begin{proposition}
%	For all $k,r\in N$ and with $k\geq 1$, the set of classes of $k$-morphic trees
%	with radius lesser or equal than $r$ is finite.
%\end{proposition}
%\begin{proof}
%TO DO
%\end{proof}
%
%We define now the $k$-morphism relation for arbitrary graph with constantss. 
%If $G^1=(V^1,E^1,\clist)$ and $G^2=(V^2,E^2,\clist)$ are graph with constantss with
%the same constants, to avoid confusion we will denote by $c_{i_j}^1$ and $c_{i_j}^2$
%the vertices labeled $c_{i_j}$ in $G^1$ and $G^2$ respectively. 
%
%\begin{definition}
%	Let $G^1=(V^1,E^1,c_{i_1}[x^1_1],\dots, c_{i_m}[x_m^1])$ and  $G^2=(V^2,E^2,c_{i_1}[x^1_2],$ 
%	$\dots, c_{i_m}[x_m^2])$ be graph with constantss with the same constant symbols. 
%	We will say that they are $k$-morphic (denoted by $G^1 \morph{k}G^2$) if there is
%	a bijection $f: V(Center(G^1))\rightarrow V(Center(G^2))$ such that
%	\begin{itemize}
%		\item ``$f$ preserves edges"
%		\[\forall x,y\in V(Center(G^1)): \quad  x\sim y \iff f(x)\sim f(y). \]
%		\item ``$f$ preserves labels"
%		\[\forall j\in \{1,\dots,m\}: \quad f(x^1_j) = x^2_j.\]
%		\item ``$f$ preserves $k$-morphism classes of trees"
%		\[\forall x\in V(Center(G^1)): \quad  Tree(x,G^1)\morph{k} Tree(f(x),G^2).\]
%	\end{itemize}
%	In this case we will say that $G^1 \morph{k} G^2$ via $f$. 	
%\end{definition}
%
%We are going to show that the rank $k$ type of a random graph a.a.s only 
%depends on the neighborhoods of its small cycles. In consequence the following definition
%is motivated:
%
%\begin{definition} 
%	Let $G=(V,E,\clist)$ be a graph with constants. Then its core of radius $r$, $Core(G,r)$
%	is the co-labeled subgraph $N(X;r)$, where $X$ is the union of the (vertex sets of the)
%	cycles in $G$ with size at most $2r+1$ and all of the labeled vertices in $G$. 
%\end{definition}
%
%
\section{Random Hyper-graphs}

Work has been done to generalize zero-one laws and limit laws of graphs to the
setting of random hyper-graphs. The results in \cite{shelah1988zero} from Shelah
and Spencer have been partially generalized for random $c$-uniform hypergraphs
in \cite{zeroonehyper}, and a some limit laws, including one for $p(n)=(n^{1-c})$
have been obtained in \cite{salvadorbrasil} using approaches different
from the ones appearing here.

@@

\begin{definition} 
	Let $p=(p_1,\dots, p_c)$, where all $p_i$'s are real numbers
	between $0$ and $1$. 
	The random model $HG(n,p)$ with edge colors $1,\dots,c$,
	sizes $a_1,\dots,a_c$, 
	symmetry groups $\Phi_1,dots,\Phi_c$ 
	and restrictions $A_1,\dots,A_c$, is the one that
	assigns to each graph $G=([n], H_1,\dots, H_c)$
	probability
	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
	\]
	Equivalently, this is the probability space obtained by 
	assigning to each colored edge 
	$e\in \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ probability $p_i$ independently. 
\end{definition}

@@

\section{The Theorem}
